Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-12-05 dsn-2018/bare_conf.tex
Added comma
Signed-off-by: Alexander Scheel <alexander.m.scheel@gmail.com>

In order to help the community build upon or work, and for the
purposes of reproducability and ascertainment of correctness the
research, data, and all associated code are provided on an open access
and open source basis under the GNU General Public License Version 3
\footnote{\url{https://www.gnu.org/licenses/gpl-3.0.en.html}}.
The code itself is hosted on GitHub at \url{https://github.com/XXXXXXXXXXXXXXXXXX}.
For additional details or to request data associated with the project, please
contact the authors.

>>>>

In order to help the community build upon or work, and for the
purposes of reproducability and ascertainment of correctness, the
research, data, and all associated code are provided on an open access
and open source basis under the GNU General Public License Version 3
\footnote{\url{https://www.gnu.org/licenses/gpl-3.0.en.html}}.
The code itself is hosted on GitHub at \url{https://github.com/XXXXXXXXXXXXXXXXXX}.
For additional details or to request data associated with the project, please
contact the authors.
